A Sound and Complete Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2024-01-10 paper/COLA/paper.tex
Minor fixes

\paragraph{Canonical model construction} The second part of a Henkin style completeness proof for modal logic
is the construction of the cannonical model. The cannonical model
$\mathcal{M} = \langle\mathcal{F},\mathcal{V}\rangle$ is such that:
\begin{itemize}
  \item The frame $mathcal{F} = \langle W, \mathcal{R}\rangle$ is
        \begin{itemize}
          \item $\mathcal{W}$ is the set of all maximal consistent sets of formulas;
          \item $\mathcal{R}(w_{1},w_{2})$ iff $\Box \varphi \in w_{1}$ implies $\varphi \in w_{2}$;
        \end{itemize}
  \item The labelling function $\mathcal{V}$ is such that $\mathcal{V}(A) \in \mathcal{W}$ and $p\in \mathcal{V}(A)$,
        for all propositional variables $A$.
\end{itemize}

>>>>

\paragraph{Canonical model construction} The second part of a Henkin style completeness proof for modal logic
is the construction of the cannonical model. The cannonical model
$\mathcal{M} = \langle\mathcal{F},\mathcal{V}\rangle$ is such that:
\begin{itemize}
  \item The frame $\mathcal{F} = \langle W, \mathcal{R}\rangle$ is
        \begin{itemize}
          \item $\mathcal{W}$ is the set of all maximal consistent sets of formulas;
          \item $\mathcal{R}(w_{1},w_{2})$ iff $\Box \varphi \in w_{1}$ implies $\varphi \in w_{2}$;
        \end{itemize}
  \item The labelling function $\mathcal{V}$ is such that $\mathcal{V}(A) = w$, $A\in w$,
        for some propositional variable $A$ and $w \in \mathcal{W}$.
\end{itemize}
